Leveraging Diversity to Find Bugs in JavaScript Engines

### 2020-06-05 paper/SQJ/old_version.tex

%\documentclass[final,5p,times,twocolumn]{elsarticle}
\documentclass[smallextended]{svjour3}
%\biboptions{numbers,sort&compress}
%\documentclass[sigconf,review, anonymous]{acmart}
%\hyphenation{on-tol-o-gy ad-di-tion-al in-fra-struc-ture an-a-lyze a-nal-y-sis}
%\input{packages}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Comment the \draftmodetrue line before submission
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifdraftmode
\draftmodetrue

%% avoid footnotes across pages
\interfootnotelinepenalty=10000
%\raggedbottom

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Uncomment \showsplattexttrue to show text from our splat paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifshowsplattext
%\showsplattexttrue

@@

%% paragraphs within margins
\usepackage[english]{babel}
\setlength{\emergencystretch}{2pt}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\usepackage{xspace}
\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
\usepackage{listings}
\usepackage[caption=false, font=footnotesize]{subfig}
%%%%%%%%%%%%% code listing
\renewcommand{\ttdefault}{pcr}
\lstset{
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\scriptsize\ttfamily\bfseries,
  language=Java,             % choose the language of the code
  frame=single,              % adds a frame around the code
  aboveskip=0pt,
  belowskip=0pt,
  breaklines=true,           % sets automatic line breaking
  breakatwhitespace=false,   % sets if automatic breaks should only happen at
  showspaces=false,
  %numbersep=5pt,              % Abstand der Nummern zum Text
  %tabsize=2,                  % Groesse von Tabs
  %extendedchars=true,         %
  %breaklines=true,            % Zeilen werden Umgebrochen
  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
}
\usepackage{balance}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{url}

\input{macros}

@@

%\title{Leveraging Diversity to Find Bugs in JavaScript Engines}
\title{Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing}
%\titlerunning{Leveraging Diversity to Find Bugs in JavaScript Engines}        % if too long for running head

\author{Igor Lima \and Breno Miranda\footnotemark \and Marcelo d'Amorim}
%\authorrunning{Short form of author list} % if too long for running head

@@

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

%\institute{Corresponding author.}

%\renewcommand{\shortauthors}{Lima et al.}

@@

\begin{abstract}
  \input{abstract}
  %\keywords{Diversity \and Test Transplantation \and Differential Testing \and JavaScript}
  \keywords{Test Transplantation \and Differential Testing \and JavaScript}
\end{abstract}

@@

%% WHAT WE DID
This work, which is empirical in nature, reports on a study to evaluate
the ability of two testing techniques to expose bugs in JavaScript engines.

%\vspace{-1ex}
%noitemsep,
\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
\item \emph{Test transplantation}.
  This technique evaluates the effect of running test files
  written for a given engine in other engines. The intuition is that
  developers design test cases with different objectives in mind. As
  such, replaying these tests in different engines could reveal
  unanticipated problems.

\item \emph{Cross-engine differential testing}.
  This technique fuzzes existing test
  inputs~\cite{fuzz-testing-history} and then compares the output
  produced by different engines using a differential
  oracle. The intuition is that interesting inputs can be created
  from existing inputs and multiple engines can be used to address the
  lack of oracles.
\end{itemize}

@@

%One of
%various causes of output discrepancy is a bug.

%% It automates test generation in scenarios where multiple
%% implementations of a system exist. DT leverages diversity across
%% system's implementations to detect anomalous behavior.
%\emph{Related Ideas.}~The idea of test set diversity dates back to the
%eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
%to prior work on this topic, this paper explores diversity of
%implementations and diversity of sources of test cases as opposed to
%diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
%elaborates related work on this topic.
%
\emph{Related Ideas.}~Differential Testing~\cite{Brumley-etal-ss07} (DT)
has been applied in a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of a
given build of their \smonkey\ engine (\eg{}, trying to enable or not
eager JIT compilation\footnote{These files are created with the
  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
is that it can be fully automated---as only one engine is used, the
outcomes of the test in both configurations are expected to be
identical. The Mozilla team uses this approach since 2002; they have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). Variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of the techniques aforementioned in finding bugs
on \javascript\ engines.

%% This paper evaluates the benefits of
%% test case diversity and engine diversity in finding bugs on
%% \javascript\ engines.

%% Recently, Patra and
%% Pradel~\cite{patra2016learning} proposed a language-agnostic fuzzer to
%% find cross-browser HTML+JS discrepancies. The main difference of our
%% work to theirs is in goal; our goal is to evaluate ability and cost of
%% simple diversity-aware approaches to find bugs in \js\ engines.

%% Their main contribution was
%% analytical whereas our main contribution is empirical--

\begin{figure}[t]
%  \vspace{-2ex}
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.\Gustavo{Não esquecer de atualizar as figuras.
  }]{
    \includegraphics[trim=0 190 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}
  }
  \caption{\label{fig:summary}Summary of bug reports.}
  \vspace{-3ex}
\end{figure}

\sloppy \emph{Results.}~We considered the following engines--\chakra{}
(Microsoft), JavaScriptCore (Apple), \veight{} (Google),
\smonkey{} (Mozilla), and \hermes (Facebook). Figure~\ref{fig:summary} shows the breakdown of bug reports per engine (\ref{fig:stacked-engine}) and per technique
(\ref{fig:stacked-technique}).
Each stacked bar breaks down the bugs
per status (\eg{}, ``1-New''). The prefix number indicates the
ordering that status labels are assigned. Several of these
reports have the label ``3-Fixed'', indicating that bug fixes have
been incorporated into the code already. Note that most of these bugs
affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
reported \noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
Furthermore, our results show that both techniques revealed several
bugs, most of which confirmed by developers. Test transplantation
revealed \noBugsTransplantation{} bugs (of which,
\noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of bug reports were similar, if we consider only those
confirmed or fixed. Most bugs we found are of moderate severity.

%% Considering cost per bug found, we found that test
%% transplantation, compared to differential testing, demanded less
%% effort from the developers who inspected the alarms.

%% All in all, these simple techniques
%% seem promising to improve reliability of engines that continuously
%% evolve with their specifications.

@@

%% LIST OF CONTRIBUTIONS
\emph{Contributions.}~The most important contribution of this work is empirical:
we provide a comprehensive study analyzing the effectiveness of
test transplantation and differential testing
in revealing functional bugs in popular \javascript\ engines.
Additional contributions are:
1)~A number of bugs found and fixed.
We reported a total of \totalBugsReported{} bugs.
Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed.
2)~An infrastructure for performing test transplantation and differential testing.
Both the scripts to run the experiments and the data processed are publicly available at \dataRepo{}.

\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
that exploring test transplantation and differential testing
should be encouraged to find functional bugs
in JavaScript engines.

@@

%% In the following, we briefly describe different sources of
%% discrepancies that can emerge across different engine implementations
%% as results of the active changes in the \es{} specification.
%% .........
%% A compatibility table relating features and supporting engines is
%% publicly available~\cite{kangax}.

The specification of JavaScript is incomplete for different
reasons. Certain parts of the specification are undefined; it is
the responsibility of engineers to decide how to implement these
functionalities. The JavaScript spec uses the label
``implementation-dependent'' to indicate these cases, where behavior
may differ from engine to engine. One reason this flexibility in the
spec exists to enable compiler optimizations. For example, the
\js\ \mcodeid{for-in} loop construct does not clearly specify the
iteration order of
elements~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that for loop
optimizations~\cite{for-in-undefined}.  As another example, the
specification states that if the \mcodeid{Number.toPrecision()}
function is called with multiple arguments then the floating-point
approximation is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like these exist in the specification. Given the speed the
specification changes and the complexity of the language some features
are not fully implemented as can be observed by the Kangax
compatibility table~\cite{kangax}.  It is also worth noting that, as
in other languages, some elements in JS have non-deterministic
behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
that makes decisions based on these elements could, in principle,
produce different outcomes on different runs. Carefully-written test
cases should not manifest this kind of flaky behavior.  As previously
mentioned, all those aspects make testing \js\ engines challenging.

%\subsection{Randomness}

%\subsection{\Fix{Other}}

%% 1) The stack depth in JS is often close to the real (native) C stack
%% depth, nevertheless observable by JS through recursion. This causes
%% differential behavior even on the same engine when JITs are enabled or
%% disabled, as the stack frame sizes vary. LangFuzz in particular
%% produces a lot of recursions and hits these problems even more often
%% than jsfunfuzz.\Mar{ask C. Holler. it is unclear to me how the output
%%   could be different.}

%% \section{Objects of Study}
%% This section discusses the objects we used in our study.

@@

%% Table~\ref{tab:engines} shows the engines we selected in this
%% study. We made an exception to the second criterion with
%% XS~\cite{xs2018repo}. As the project is young, created in Oct 2017, we
%% thought there was insufficient time to obtain 1K stars for XS. We
%% still considered this project as it seems to be attracting interest
%% from the community\Fix{is this true?}

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:engines}Engines selected.}
  \begin{tabular}{cccrrr}
    \toprule
    Team & Name & URL & \# Stars  & DOB & Version \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} & 3300+ & Jun 2001 & xxxx\\
    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008 & 8.4.138\\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009 & xxxx\\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} & 1100+ & Mar 1996 & 76.0b6\\
    Facebook & \hermes & \cite{hermes2020repo} & 5400+ & Jul 2019 & 0.5.0\\
   \bottomrule
  \end{tabular}
\end{table}

% hermes very first commit: https://github.com/facebook/hermes/commit/f22a18f67da3f03db59c1ec715d6ec3776b03fbf

@@

%% accessible from GitHub using the GitHub REST
%% API~\cite{github-rest-api}.

@@

\newcommand\marktopleft[1]{%
    \tikz[overlay,remember picture]
        \node (marker-#1-a) at (0,2ex) {};%
}
\newcommand\markbottomright[1]{%
    \tikz[overlay,remember picture]
        \node (marker-#1-b) at (0,0) {};%
    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};%
}

@@

%% The main source of test
%% cases is the official Test262~\cite{tc39-github} conformance test
%% suite for the ECMA262 specification~\cite{ecmas262-spec}.\Comment{
%%   This test suite contains 87\% of all the tests we used.} We also
%% considered test suites of three of the four engines mentioned in
%% Section~\ref{sec:methodology:engines} and four other engines. Overall,
%% we selected a total of \totfiles{} JS
%% files.

@@

%% With that mapping it is
%% possible to measure distance between two sentences as the distance
%% between the vectors characterizing them. Consequently, one can
%% measure, for example, the minimum distance between a sentence in
%% English and a sentence in a \js\ embedding, built with word2vec using
%% a corpus of \js\ sentences. \Mar{Please confirm if this is the idea!
%%   If yes, shouldn't just one corpus (e.g., the JS corpus) be enough to
%%   solve the problem? Are there two separate embeddings (one for
%%   English and one for JS)? If not, how they are combined? What about
%%   the classification scheme?  It needs to answer yes/no (not a
%%   distance).}

>>>>

\documentclass[smallextended]{svjour3}

\newif\ifdraftmode
\draftmodetrue

\interfootnotelinepenalty=10000

\newif\ifshowsplattext

@@

\usepackage[english]{babel}
\setlength{\emergencystretch}{2pt}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tikz}
\usetikzlibrary{matrix,fit,shapes,calc,positioning,shadows,arrows,shapes,backgrounds,decorations.markings,fadings}
\usepackage{listings}
\usepackage[caption=false, font=footnotesize]{subfig}
\renewcommand{\ttdefault}{pcr}
\lstset{
  basicstyle=\scriptsize\ttfamily,
  keywordstyle=\scriptsize\ttfamily\bfseries,
  language=Java,             
  frame=single,              
  aboveskip=0pt,
  belowskip=0pt,
  breaklines=true,           
  breakatwhitespace=false,   
  showspaces=false,
  keywords=[2]{class, incorporateUserFeedback, testPushPop, testPopPush},
}
\usepackage{balance}
\usepackage{wrapfig}
\usepackage{enumitem}
\usepackage{url}

\newcommand{\js}{JS}
\newcommand{\javascript}{JavaScript}
\newcommand{\es}{ES}
\newcommand{\ecmascript}{\es{}}
\newcommand{\tname}{TNAME}
\newcommand{\Comment}[1]{}
\newcommand{\numsubjects}{5}
\newcommand{\etal}{and colleagues'}
\newcommand{\ie}{i.e.}
\newcommand{\eg}{e.g.}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{{\color{red}\ding{55}}}
\newcommand{\pGoodGood}{$\mathit{P}${\small\cmark\!\cmark}}
\newcommand{\pGoodBad}{$\mathit{P}${\small\cmark\!\xmark}}
\newcommand{\pBadDontCare}{$\mathit{P_?}$}
\newcommand{\sfl}{SFL\xspace}
\newcommand{\ddg}{DDG\xspace}
\newcommand{\totfiles}{$\sim$38K}

\newif\ifdraftmode
\draftmodetrue
\ifdraftmode
 \newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
 \newcommand{\Mar}[1]{\textbf{[[Marcelo: }{\color{magenta} #1}\textbf{]]}}
 \newcommand{\Igor}[1]{\textbf{[[Igor: }{\color{blue} #1}\textbf{]]}}
 \newcommand{\notes}[1]{\todo[inline,color=red!30,caption={}]{#1}}
\else
 \newcommand{\Fix}[1]{\relax}
 \newcommand{\Mar}[1]{\relax}
 \newcommand{\Igor}[1]{\relax}
 \newcommand{\notes}[1]{\relax}
\fi

\newcommand{\codesize}{\small}
\newcommand{\CodeIn}[1]{\mcodeid{#1}}
\newcommand{\CodeInM}[1]{\mcodeid{#1}}
\def\|#1|{\mathid{#1}}
\newcommand{\mathid}[1]{\ensuremath{\mathit{#1}}}
\def\<#1>{\codeid{#1}}
\newcommand{\codeid}[1]{\ifmmode{\mbox{\codesize\ttfamily{#1}}}\else{\codesize\ttfamily #1}\fi}
\def\<#1>{\mcodeid{#1}}
\newcommand{\mcodeid}[1]{\mbox{\codesize\ttfamily{#1}}}
\newcommand{\CodeInSmaller}[1]{\mbox{\scriptsize\ttfamily{#1}}}

\newcommand*{\RightThumbsUpAux}[1]{
  \begingroup
    \sbox0{Ag}
    \raisebox{-\dp0}{
      \includegraphics[{
        height=\dimexpr\dp0+\ht0\relax,
        #1
      }]{thumbsup.pdf}
    }
  \endgroup
}
\newcommand*{\RightThumbsUp}{
  \RightThumbsUpAux{}
}
\newcommand*{\RightThumbsDown}{
  \RightThumbsUpAux{origin=c,angle=180}
}
\newcommand*{\LeftThumbsUp}{
  \scalebox{-1}[1]{\RightThumbsUp}
}
\newcommand*{\LeftThumbsDown}{
  \scalebox{-1}[1]{\RightThumbsDown}
}

\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}

\newcommand{\totalTestFiles}{40,041} 
\newcommand{\totalTestFilesPassInPar}{7,061} 
\newcommand{\totalTestFilesCompileInAll}{36,448} 
\newcommand{\totalTestFilesPassInAll}{23,808} 
\newcommand{\totalTestFilesForTestTransplantation}{6,602}

\newcommand{\nofuzzAll}{209}
\newcommand{\nofuzzBugs}{\Fix{XX}}
\newcommand{\nofuzzDuplicates}{63}
\newcommand{\nofuzzFalsePositives}{24}
\newcommand{\nofuzzHITotal}{177}
\newcommand{\nofuzzLOTotal}{32}
\newcommand{\nofuzzTotalFiles}{977} 
\newcommand{\nofuzzFilesHI}{940} 
\newcommand{\nofuzzFilesLO}{37} 
\newcommand{\nofuzzBucketsBugsHI}{\Fix{124}} 
\newcommand{\nofuzzBucketsBugsLO}{\Fix{11}} 
\newcommand{\nofuzzDupsHI}{\Fix{X}}
\newcommand{\nofuzzDupsLO}{\Fix{Y}}
\newcommand{\tableBugsNum}{\Fix{26}}

\newcommand{\noBugsTransplantation}{28}
\newcommand{\noBugsTransplantationConfirmed}{20}
\newcommand{\noBugsTransplantationFixed}{12}

\newcommand{\noBugsDifferentialTesting}{22}
\newcommand{\noBugsDifferentialTestingConfirmed}{16}
\newcommand{\noBugsDifferentialTestingFixed}{10}

\newcommand{\totalBugsReported}{49}
\newcommand{\totalBugsConfirmed}{33}
\newcommand{\totalBugsFixed}{22}

\newcommand{\noBugsBugsReportedGoogle}{five}
\newcommand{\noBugsBugsConfirmedGoogle}{four}

\newcommand{\percChakra}{\Fix{52\%}} 
\newcommand{\percJSC}{\Fix{45\%}}

\newcommand{\noTransConfirmed}{18}
\newcommand{\noTransSeverityTwo}{16}
\newcommand{\noTransChakraBugs}{13}
\newcommand{\noTransChakraBugsFixed}{7}
\newcommand{\noTransVeightBugsConfirmed}{two}
\newcommand{\noTransVeightBugsReported}{three}
\newcommand{\noTransVeightBugsFixed}{two}

\newcommand{\noTransUndefined}{204} 
\newcommand{\noTransTimeout}{23} 
\newcommand{\noTransNotImplemented}{54} 
\newcommand{\noTransNonStandard}{122} 
\newcommand{\noTransOther}{174} 
\newcommand{\noTransTPDuplicated}{11} 
\newcommand{\noTransTPBugs}{24}

\newcommand{\noDiffConfirmed}{fifteen}
\newcommand{\noDiffFixed}{ten}
\newcommand{\noDiffVeight}{2}
\newcommand{\noDiffVeightConfirmed}{2}
\newcommand{\noDiffVeightFixed}{1}

\newcommand{\warningsIteration}{five}

\ifdraftmode
\newcommand{\anonym}[1]{{\tiny\colorbox{black}{xxx}}}
\else
\newcommand{\anonym}[1]{{\tiny\colorbox{black}{#1}}}
\fi

\newcommand{\radamsa}{radamsa}
\newcommand{\quickfuzz}{quickfuzz}

\newcommand{\jsc}{JSC}
\newcommand{\veight}{V8}
\newcommand{\chakra}{Chakra}
\newcommand{\smonkey}{SpiderMonkey}
\newcommand{\jerry}{JerryScript}

\newcommand{\lo}{lo}
\newcommand{\hi}{hi}

\newcommand{\testsThatFail}{63}
\newcommand{\testsThatFailJSC}{6}
\newcommand{\testsThatFailSM}{57}
\newcommand{\filesAttached}{490}
\newcommand{\filesAttachedSM}{110}
\newcommand{\filesAttachedJSC}{10}
\newcommand{\filesAttachedVeight}{370}
\newcommand{\filesMining}{1,240}
\newcommand{\filesMiningSM}{377}
\newcommand{\filesMiningJSC}{224}
\newcommand{\filesMiningVeight}{639}
\newcommand{\samplesEnglish}{25K}
\newcommand{\samplesJSSnippets}{25K}
\newcommand{\accuracyMining}{98\%}

\newcommand{\percentSuiteTestJSC}{92\%}
\newcommand{\percentSuiteTestVeight}{95\%}
\newcommand{\percentSuiteTestChakra}{75\%}
\newcommand{\percentSuiteTestSM}{93\%}

\newcommand{\failuresTestTrans}{836}
\newcommand{\failuresTestTransDistictFiles}{612} 
\newcommand{\failuresTestTransPercent}{9.2\%}
\newcommand{\noBugsTransplantationSeverityTwo}{16}
\newcommand{\bugsChakra}{12}
\newcommand{\bugsChakraFixed}{3}

\newcommand{\testOriginal}{31,276} 
\newcommand{\testPassInPar}{-}
\newcommand{\testCompileAll}{29,846} 
\newcommand{\testNoFailAll}{17,639}

\newcommand{\veightOriginal}{1,084} 
\newcommand{\veightPassInPar}{482} 
\newcommand{\veightCompileAll}{478} 
\newcommand{\veightNoFailAll}{426}

\newcommand{\smOriginal}{3,122} 
\newcommand{\smPassInPar}{2,155} 
\newcommand{\smCompileAll}{2,103} 
\newcommand{\smNoFailAll}{1,837}

\newcommand{\jscOriginal}{1,265} 
\newcommand{\jscPassInPar}{1,130} 
\newcommand{\jscCompileAll}{1,122} 
\newcommand{\jscNoFailAll}{1,054}

\newcommand{\duktapeOriginal}{1,195}
\newcommand{\duktapePassInPar}{1,195}
\newcommand{\duktapeCompileAll}{921}
\newcommand{\duktapeNoFailAll}{915}

\newcommand{\jerryOriginal}{1,951}
\newcommand{\jerryPassInPar}{1,951}
\newcommand{\jerryCompileAll}{1,878}
\newcommand{\jerryNoFailAll}{1,837}

\newcommand{\jsiOriginal}{99}
\newcommand{\jsiPassInPar}{99}
\newcommand{\jsiCompileAll}{63}
\newcommand{\jsiNoFailAll}{63}

\newcommand{\tinyOriginal}{49}
\newcommand{\tinyPassInPar}{49}
\newcommand{\tinyCompileAll}{37}
\newcommand{\tinyNoFailAll}{37}

\newcommand{\dataRepo}{\url{https://figshare.com/s/ee2e3821c2f022c7f5cc}}

@@

\title{Leveraging Diversity to Find Bugs in JavaScript Engines}

\author{Igor Lima \and Breno Miranda\footnotemark \and Marcelo d'Amorim}

@@

\date{Received: date / Accepted: date}

@@

\begin{abstract}
  \textbf{Context.} JavaScript is a very popular programming language today with several
implementations competing for market dominance. Although a
specification document and a conformance test suite exist to guide
engine development, bugs occur and have important practical
consequences. Implementing correct
engines is challenging because the spec is intentionally
incomplete and evolves frequently.
\textbf{Objective.} This paper evaluates the importance of
diversity to find functional bugs in JavaScript engines. \textbf{Method.} For that, we
studied two existing diversity-aware techniques---test transplantation and
cross-engine differential testing. The first technique runs test
suites of a given engine in another engine. The second technique
fuzzes existing inputs and then compares the output produced by
different engines with a differential oracle.
\textbf{Results.} We considered engines from four major players in our
experiments--Apple, Google, Microsoft, and Mozilla. Our results
indicate that both techniques revealed several bugs, many of which
confirmed by developers. We reported \noBugsTransplantation{} bugs
with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
confirmed and \noBugsTransplantationFixed{} fixed) and reported
\noBugsDifferentialTesting{} bugs with differential testing
(\noBugsDifferentialTestingConfirmed{} of these confirmed
and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
most of these bugs affected two engines--Apple's
\jsc{} and Microsoft's \chakra{}. To summarize, our results show that
diversity-aware techniques are easy to apply and very effective in
finding bugs in complex software, such as JavaScript engines.
   \keywords{Diversity \and Test Transplantation \and Differential Testing \and JavaScript}
\end{abstract}

@@

This work, which is empirical in nature, reports on a study to evaluate the importance of diversity
to find bugs in JavaScript engines; it covers two complementary
diversity-aware testing techniques.

\begin{itemize}[topsep=0pt,parsep=0pt,partopsep=2pt,labelwidth=0cm,align=left,itemindent=-0.25cm]
\item \emph{Test transplantation} leverages diversity of test
  cases. This technique evaluates the effect of running test files
  written for a given engine in other engines. The intuition is that
  developers design test cases with different objectives in mind. As
  such, replaying these tests in different engines could reveal
  unanticipated problems.

\item \emph{Cross-engine differential testing} leverages diversity of
  engine implementations. This technique fuzzes existing test
  inputs~\cite{fuzz-testing-history} and then compares the output
  produced by different engines.\Comment{ using a differential
    oracle.} The intuition is that interesting inputs can be created
  from existing inputs and multiple engines can be used to address the
  lack of oracles.
\end{itemize}

@@

\emph{Related Ideas.}~The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980,ostrand-balcer-1988}. In contrast
to prior work on this topic, this paper explores diversity of
implementations and diversity of sources of test cases as opposed to
diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
elaborates related work on this topic. Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of a
given build of their \smonkey\ engine (\eg{}, trying to enable or not
eager JIT compilation\footnote{These files are created with the
  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
is that it can be fully automated---as only one engine is used, the
outcomes of the test in both configurations are expected to be
identical. The Mozilla team uses this approach since 2002; they have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum up, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of the techniques aforementioned in finding bugs
on \javascript\ engines.

\begin{figure}[t]
  \centering
  \subfloat[\label{fig:stacked-engine}Bug reports per engine.]{
    \includegraphics[trim=0 190 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-engine}
    \vspace{-5ex}
  }\\
  \subfloat[\label{fig:stacked-technique}Bugs reports per technique.]{
    \includegraphics[trim=0 180 0 180,clip,width=0.7\textwidth,scale=0.4]{R/stackedbar/stacked-technique}
    \vspace{-5ex}        
  }
  \caption{\label{fig:summary}Summary of bug reports.}
  \vspace{-3ex}
\end{figure}

\sloppy \emph{Results.}~We considered the following engines--\chakra{}
(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
bug reports per engine (\ref{fig:stacked-engine}) and per technique
(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
per status (\eg{}, ``1-New''). The prefix number indicates the
ordering that status labels are assigned. Several of these
reports have the label ``3-Fixed'', indicating that bug fixes have
been incorporated into the code already. Note that most of these bugs
affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
reported \noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
Furthermore, our results show that both techniques revealed several
bugs, most of which confirmed by developers. Test transplantation
revealed \noBugsTransplantation{} bugs (of which,
\noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of bug reports were similar, if we consider only those
confirmed or fixed. Most bugs we found are of moderate severity.

@@

\emph{Contributions.}~The most important contribution of this work is empirical: 
we provide a comprehensive study analyzing the effectiveness of diversity-aware
techniques to find functional bugs in popular \javascript\ engines.
Additional contributions are:
1)~A number of bugs found and fixed. 
We reported a total of \totalBugsReported{} bugs. 
Of these, \totalBugsConfirmed{} bugs were confirmed and \totalBugsFixed{} bugs were fixed. 
2)~An infrastructure for diversity-aware testing.
The scripts to run the experiments will be available upon request. 
The data is publicly available \dataRepo{}.

\vspace{1ex} To summarize, this paper provides initial, yet strong evidence
that exploring diversity should be encouraged to find functional bugs
in JavaScript engines.

@@

The specification of JavaScript is incomplete for different
reasons. Certain parts of the specification are undefined; it is
responsibility of engineers to decide how to implement these
functionalities. The JavaScript spec uses the label
``implementation-dependent'' to indicate these cases, where behavior
may differ from engine to engine. One reason this flexibility in the
spec exists is to enable compiler optimizations. For example, the
\js\ \mcodeid{for-in} loop construct does not clearly specify the
iteration order of
elements~\cite{so-forin-undefined,javascript-in-chrome} and different
engines capitalize on that for loop
optimizations~\cite{for-in-undefined}.  As another example, the
specification states that if the \mcodeid{Number.toPrecision()}
function is called with multiple arguments then the floating-point
approximation is
implementation-dependent~\cite{es6-toPrecision}. Various other cases
like these exist in the specification. Given the speed the
specification changes and the complexity of the language some features
are not fully implemented as can be observed by the Kangax
compatibility table~\cite{kangax}.  It is also worth noting that, as
in other languages, some elements in JS have non-deterministic
behavior (\eg{}, \mcodeid{Math.random} and \mcodeid{Date}). A test
that make decisions based on these elements could, in principle,
produce different outcomes on different runs. Carefully-written test
cases should not manifest this kind of flaky behavior.  As previously
mentioned, all those aspects make testing \js\ engines challenging.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:engines}Engines selected.}
  \begin{tabular}{cccrr}
    \toprule
    Team & Name & URL & \# Stars  & DOB \\
    \midrule
    Apple & \jsc{} (WebKit) & \cite{jsc2018repo} &
    \multicolumn{1}{c}{3300+} & Jun 2001\\
    Google & \veight{} & \cite{v82018repo} & 9800+ & Jun 2008\\
    Microsoft & \chakra{} & \cite{chakra2018repo} & 7200+ & Nov 2009\\
    Mozilla & \smonkey{} & \cite{spidermonkey2018repo} &
    \multicolumn{1}{c}{1100+} & Mar 1996\\
   \bottomrule     
  \end{tabular}
\end{table}

@@

@@

\newcommand\marktopleft[1]{
    \tikz[overlay,remember picture] 
        \node (marker-#1-a) at (0,2ex) {};
}
\newcommand\markbottomright[1]{
    \tikz[overlay,remember picture] 
        \node (marker-#1-b) at (0,0) {};
    \tikz[overlay,remember picture,thick,dashed,inner sep=2pt]
        \node[draw,rectangle,fit=(marker-#1-a.center) (marker-#1-b.center)] {};
}

@@

@@
